---
title: "STAT XXX HW 1"
author: "Your Name Here"
date: "`r Sys.Date()`"
output: pdf_document
header-includes:
  - \usepackage{hayesmacros}
---

```{r include = FALSE}
knitr::opts_chunk$set(
  echo = FALSE,          # don't show code
  warning = FALSE,       # don't show warnings
  message = FALSE,       # don't show messages (less serious warnings)
  cache = TRUE,          # save results from last compilation
  fig.align = "center"   # center figures
)

library(tidyverse)       # load libraries you always use here
library(tidymodels)
library(knitr)           # require for purl function to create code appendix
library(hayeslib)        # i highly recommend creating a personal R package
                         # with code you use a lot and loading it here as well

set.seed(27)             # make random results reproducible

this_file <- "template.Rmd"  # used to automatically generate code appendix
```

## Notes on the YAML header

- Be sure to change the title and author fields
- The date is automatically set to the current day when knitting
- The `header-includes` portion loads a personal sheet of LaTeX macros. I recommend making one of these as well as it can greatly speed up the time to input math. See my personal macro file `hayesmacros.sty` as a starting point. If you aren't going to load a \LaTeX macro file, remove those lines.
    - `hayesmacros.sty` needs to be in the same folder as this file


# Problem 1

Your homework goes here

# Code

```{r code = readLines(purl(this_file, documentation = 1)), echo = T, eval = F}
# this R markdown chunk generates a code appendix
```
