---
title: "STAT XXX HW 1"
author: "Your Name Here"
date: "`r Sys.Date()`"
output:
  pdf_document: default
  html_document:
    highlight: tango
urlcolor: blue
header-includes: \usepackage{hayesmacros}
---

```{r include = FALSE}
knitr::opts_chunk$set(
  echo = FALSE,                 # don't show code
  warning = FALSE,              # don't show warnings
  message = FALSE,              # don't show messages (less serious warnings)
  cache = FALSE,                # set to TRUE to save results from last compilation
  fig.align = "center",         # center figures
  attr.source = '.numberLines'  # add line numbers to code
)

library(tidyverse)       # load libraries you always use here

set.seed(27)             # make random results reproducible
```

## Notes on the YAML header

- Be sure to change the title and author fields
- The date is automatically set to the current day when knitting
- The `header-includes` portion loads a personal sheet of LaTeX macros. I recommend making one of these as well as it can greatly speed up the time to input math. See my personal macro file `hayesmacros.sty` as a starting point. If you aren't going to load a \LaTeX macro file, remove those lines.
    - `hayesmacros.sty` needs to be in the same folder as this file

# Problem 1

Here is a [link](https://adv-r.hadley.nz/). Your homework goes here.

Briefly, some of the custom latex macros: $y = \b x + \e$. Also, some code:

```{r}
fit <- lm(hp ~ ., mtcars)
au <- broom::augment(fit)

au %>% 
  gather(x, val, -contains(".")) %>% 
  ggplot(aes(val, .resid)) + 
  geom_point() + 
  facet_wrap(~x, scales = "free")
```

Yet more text, and another code section:

```{r}
knitr::kable(head(select(au, 1:5)))
```

# Code

```{r ref.label = knitr::all_labels(), echo = TRUE, eval = FALSE}
# this R markdown chunk generates a code appendix
```
